### 2020-07-01 introduction.tex
change temp
revise by cl

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction'' than ``interpolation''. Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character.

@@

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture aiming at reconstructing extremely massive blurred and defocused snapshots. It can be further extended to other text-recognition applications on commercial smartphones.
  \item	We evaluate this new shoulder surfing attack in comprehensive scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
\end{itemize}
% describe the organization of the paper
The rest of the paper is organized as follows. Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing attack. We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}, respectively. We further wrap up this paper by presenting the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}. And the conclusion is show in Section~\ref{sec-conclusion}.

>>>>

\begin{itemize}[leftmargin=*]
  \item \textbf{Blurriness of input images.} The most prominent one is the blurriness of captured snapshots, as they are taken secretly and hurriedly at extreme range, without specially focusing. It can be further exacerbated by straining the magnification of the smartphone lenses. Unlike most SR applications and datasets working with ``normally'' captured snapshots (e.g., scenery, scanned images) \cite{nasrollahi2020deep,lyn2020image}, these snapshots exhibit lower concentrations of information and more artifacts, requiring a reliable ``reconstruction'' than ``interpolation''. Since blurrier input means less information, rendering a greater possibility of reconstructing the wrong character. 

@@

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, an end-to-end threat model of shoulder surfing from a broad range. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We design a multi-frame SR neural network architecture aiming at reconstructing extremely massive blurred and defocused snapshots. It can be further extended to other text-recognition applications on commercial smartphones.
  \item	We evaluate this new shoulder surfing attack in comprehensive scenarios. And it outperforms the state-of-the-arts for the new privacy concern.
\end{itemize}
% describe the organization of the paper
The rest of the paper is organized as follows. Section~\ref{sec-related-work} describes the related work, especially the state-of-the-arts for the shoulder surfing and SR techniques. We present the system and network design in Section~\ref{sec-design}, followed by the implementation and evaluation in Section~\ref{sec-implementation-and-training} and~\ref{sec-evaluation}. We further wrap up this paper by delivering the limitations and countermeasures of our system in Section~\ref{sec-limitations-and-discussions}. And the conclusion is shown in Section~\ref{sec-conclusion}.

### 2020-07-01 related_work.tex
change temp
revise by cl

\begin{table*}[t]
    \caption{A comparison of state-of-the-art works on shoulder surfing.}
    \vspace{2mm}
    \begin{center}
    \begin{tabular}{ccccc}
    \hline
     Reference & Subject & Range$^{\mathrm{a}}$ & Deployment & Performance\\ 
    \hline
    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
    \hline
    \textbf{\textsf{SRPeek}} & Multi-type Characters & 1.5m \& 30$^\circ$ & COTS smartphones & Recovery 95\% Contents in Real Time \\
    \hline
    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning.}\\
    \end{tabular}
    \label{comparison}
    \end{center}
\end{table*}

\section{Related Work}
\label{sec-related-work}

\cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}. To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}. Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}. Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm. To deal with the threat model of tool-assisted shoulder surfing\cl{more citations?},
% Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}
Maggi et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}. It can however only function when the attacker is standing at close range, which is a barely practical scenario. By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can successfully obtain information for a longer range to reduce suspicion. Evaluations demonstrate its feasibility and privacy concerns in our daily life.

\subsection{Super Resolution}
Image super-resolution is the process of reconstructing an image with a higher spatial resolution. Single image super-resolution techniques accept a single low-res image as input, and based on its structural pattern, self-similarity \cite{suetake2008image}, or previous knowledge of the genre of the image, deduces missing information and reconstructs the missing pixels to form a sharp, high-res image. On the other hand, multiple image super-resolution techniques work on a set of pictures on the same scene, e.g. multiple snapshots captured by the camera of a smartphone, successive images from a satellite, or adjacent frames on a video clip. These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single image super-resolution.

Over the last two decades a variety of techniques have been proposed for the multiple image super-resolution problem. Early works focus on the analysis of the images on spatial or frequency domains. One of the widely known spatial domain methods is the Shift-Add algorithm \cite{farsiu2003robust}, which functions by maximizing the pixel-wise possibility of high-res image generating low-res images. On the other hand, frequency domain approaches focus on the Fourier transform of the images. By assuming that the high-res scene is band-limited, frequency domain algorithms can reconstruct high-frequency components from patterns of the low-frequency components, removing bands of noise and blur effects at the same time. A great variety of techniques have been proposed, however, due to the nature of the problem, these algorithms are all tailored for their application: natural photos, scanned text, satellite imaging, biometrics, etc. and achieve best performance only in their own field.

More recent works of Super Resolution are often based on deep learning approaches. In 2016, SRCNN \cite{dong2015image} was developed from CNN replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches. This work focuses on single image super-resolution, as the neural network accepts a single image as input. Generative Adversarial Networks (GAN) were also used in this era\cite{ledig2017photo}, generating photo-realistic images, with less artifacts and more genuine-looking details pleasing to the human eye, though not always accurate against the real scene. When published, the above works were limited to single input images, and most multi-image SR tasks are variations of them. The most common variation is video SR\cite{shi2016real, kappeler2016video}, with a structure similar to SRCNN, accepting complete video clips as input, and functioning on the similarity between frames. The sequentiality and consistency between adjacent frames makes it easy for the convolution networks to comprehend, and by modifying the 2d convolution layers to 3d convolution\cite{caballero2017real}, modifying the dataflow to merge neighboring frames among the network layers\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame\cite{sajjadi2018frame}, the task can be completed easily. Other works face image groups without consistency or sequential information, e.g. satellite images. To achieve appreciable results, most works choose hybrid methods, solving the multi-image SR problem with multiple single-image SR procedures. They commonly function by merging the results of single image SR algorithms to efficiently utilize input information\cite{kawulok2019deep}, or building a multi-image network to create a course view and support it with single image SR networks\cite{8834937}. These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods. However, because of the extreme blurriness of the photos and the lack of consistency between frames, the methods mentioned above are not suitable for our application and we need a novel approach.

>>>>

\begin{table*}[t]
    \caption{A comparison of state-of-the-art works on shoulder surfing.}
    \vspace{2mm}
    \begin{center}
    \begin{tabular}{ccccc}
    \hline
     Reference & Deployment & Range$^{\mathrm{a}}$ & Subject & Performance\\ 
    \hline
    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
    \hline
    \textbf{\textsf{SRPeek}} & COTS smartphones & 1.5m \& 30$^\circ$ & Multi-type Characters & Real-time Monitoring with 95\% Contents\\
    \hline
    \multicolumn{5}{l}{$^{\mathrm{a}}$The maximum distance and observing view angle to the victim's screen.}\\
    \end{tabular}
    \label{tbl:comparison}
    \end{center}
\end{table*}

\section{Related Work}
\label{sec-related-work}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}. To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}. Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}\cl{more citation and table 1 row-1}. Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm. To deal with the threat model of tool-assisted shoulder surfing\cl{more citation and table 1 row-2},
% Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}
Maggi et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera~\cite{maggi2011poster}. It can however only function when the attacker is standing at close range, which is a barely practical scenario. By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can deploy it on commercial smartphones while obtaining information for a longer range to reduce suspicion, say 1.5m away from the victim's screen with an observing view of 30$^\circ$ shown in Table~\ref{tbl:comparison}. Evaluations demonstrate its feasibility and privacy concerns in our daily life.

\subsection{Super Resolution}
Image SR is the process of reconstructing an image with a higher spatial resolution. Based on the structural pattern, self-similarity~\cite{suetake2008image}, or previous knowledge of the image genre, the single-image SR techniques take as input a single low-resolution image, rendering a sharp, high-resolution one by deducing missing information and reconstructing the missing pixels. Further, multi-image SR techniques work on a set of pictures on the same scene, such as multiple snapshots captured by a smartphone, successive images from a satellite, or adjacent frames on a video clip. These algorithms collect extra data from slight differences of these redundant images, often exhibiting better performance than single-image SR algorithms. And a variety of techniques have been proposed for the multi-image SR problem. And early works focus on the analysis of images in spatial or frequency domains. For example, the Shift-Add algorithm~\cite{farsiu2003robust} analyzes the spatial information by maximizing the pixel-wise possibility of high-resolution image from low-resolution images. Besides, approaches for the frequency domain rely on the Fourier transform of images. Assuming that the high-resolution scene is band-limited, these algorithms reconstruct high-frequency components from patterns of low-frequency components, removing bands of noise and blur effects simultaneously. Unfortunately, all SR techniques  however, are subject-specific and achieve the best performance only for some contents, including natural photos, scanned text, satellite imaging, biometrics\cl{more citation and table 1 row-3}. While \textsf{SRPeek} can recover multi-type characters with complex strokes, including Chinese, English and numbers.

Deep learning approaches can also be adopted for Super Resolution. For example, SRCNN~\cite{dong2015image} was designed using CNN by replacing pooling layers with upsampling layers, achieving notably better performance than previous approaches. It however only focuses on single image SR, as the neural network accepts a single image as input\cl{table 1 row-4}. Besides, Generative Adversarial Networks (GAN) were also used to generate photo-realistic images~\cite{ledig2017photo}, with less artifacts and more genuine-looking details perceptible to the human eye. To resolve multi-image SR tasks, say video SR, existing works~\cite{shi2016real, kappeler2016video} design a structure similar to SRCNN, and accept complete video clips as input. Then the sequentiality and consistency between adjacent frames can help recover the missing pixels of clips using convolution networks, Specifically,
% modifying the 2d convolution layers to 3d convolution~\cite{caballero2017real}, 
we can modify the dataflow to merge neighboring frames among the network layers~\cite{huang2017video}, or recurrently processing the frames under the guidance of the output of the previous frame~\cite{sajjadi2018frame}\cl{table 1 row-5}.. For images without consistency or sequential information, like satellite images, most works choose hybrid methods to solve the multi-image SR problem with multiple single-image SR procedures. They either merge the results of single-image SR algorithms for efficiency~\cite{kawulok2019deep}, or build a multi-image network to create a comprehensive view based on single image SR networks~\cite{8834937}\cl{table 1 row-6}. Due of the extreme blurriness of snapshots, these methods can not deal with the new shoulder surfing threat model we proposed, which takes as input massive blurred snapshots without the consistency between frames. And they achieve limited performance, shown in Table~\ref{tbl:comparison}.
% These methods expect at least some degree of information to be extracted from each of the single frames with single image SR methods.
